\documentclass[line,margin]{res} 
\usepackage{hyperref}

\textheight=700pt

\begin{document}

\name{\Huge{Jacob M Potter} \normalsize{\sl Software Engineer}}

\begin{resume}

%-------------------------------------------------------------------------------
%   OBJECTIVE
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
Looking for a challenging computing co-op or internship for the summer of 2018.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
\section{CONTACT}
\href{mailto:jmp1617@rit.edu}{jmp1617@rit.edu}\hfill 
\href{https://jacob-potter.com}{jacob-potter.com}\\
(413) 335-7767\hfill 
\href{https://github.com/jmp1617}{github.com/jmp1617}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Rochester Institute of Technology}, Rochester, NY\hfill
    \textbf{2016-2021}\\
{\sl Bachelor of Science}, Computer Science, May 2021\hfill GPA: 3.59
\\
{\sl Dean's List} - Golisano College of Computing and Information Sciences
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
    \href{https://github.com/jmp1617/deepnet.git}{\textbf{Deepnet}}
    {\sl (C, OpenGL)}\hfill \textbf{Current}\\ 
    Multi-purpose four layer CLI deep learning neural network. Uses
    backpropegation and sigmoid activation. Features include importing and 
    exporting trained synapses and live OpenGL synapse delta visualization.
\par
    \href{https://github.com/jmp1617/lmedit.git}
    {\textbf{MIPS R2K module analyzer/editor }}{\sl (C)}\hfill \textbf{2017}\\
    Reads all sections of R2K load or object module into dynamic memory, 
    extracts the data, and then displays in human readable form. Provides the 
    option to edit the binary data in place and then write it out.
\par
    \href{https://github.com/jmp1617/LLUV.git}{\textbf{L.L.U.V.}}
    {\sl (Python 3.5)}\hfill \textbf{2017}\\ 
    L.L.U.V. (Linux Live USB Vending) is an easy to use front-end TUI for the 
    Linux command dd. I made the project available on Python Pip.
\par
    \href{https://github.com/jmp1617/ast-developer.git}{\textbf{AST-Developer}}
    {\sl (Java 8, CSS)}\hfill \textbf{2016}\\ 
    Program that allows users to create a flow of instructions with an easy to
    use interface which is then converted to abstract syntax trees. Inspired by 
    MIT Scratch.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}
\textbf{Languages}: C 99, Python (2.7-3.5), Java 8.
\\
\textbf{Networking and Security}: Cisco-3550, Wireshark, Nmap, Metasploit.  
\\
\textbf{Compilers and Tools}: GCC, Clang, GDB, Vim, Valgrind, Git, 
Jetbrains Suite. 
\\
\textbf{Operating Systems}: 
GNU+Linux, Mac OSX, Windows, Android.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{EXPERIENCE}
\employer{\textbf{Summer 2017}}
\location{Southwick, MA}
\dates{{\sl Whalley Computer Associates}}
\title{\textbf{Recieving Department}}
\begin{position}
    Responsible for recieving and keeping track of high dollar value 
    computational products for a customers. Customer base ranged from large 
    corporate institutions to medium computing security companies. Worked in a
    team based corporate environment.
\end{position}
\employer{\textbf{Summer 2016}}
\location{Belchertown, MA}
\dates{{\sl Belcertown IT Department}}
\title{\textbf{IT Intern}}
\begin{position}
    Tasked with repairing computational devices, imaging and setting up devices, 
    as well as asisting school staff with both hardware and software issues. 
    Planned and also implimented the student help desk system for the high 
    school.
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
\section{ACTIVITIES}
\href{https://csh.rit.edu}{\textbf{Computer Science House}}
{\sl (organization)}\hfill
\textbf{Current Member}\\
A special interest house at RIT which encourages group collaboration on technical 
projects and provides access and funds to develop those projects. Members have 
access to 3D printers, a member run server room, electrical prototyping 
resources, etc.\\
\textbf{Events}: 
CRTS (Red team Blue team), Opcommation (Networking Hackathon), etc.\\\\
\textbf{Other Interests/Activities}\\
MLH Brick Hack, Geocaching, Snowboarding, Archery, Lock picking, and Boy Scouts.
%-------------------------------------------------------------------------------

\end{resume}

%subscript
\scriptsize{References on request} \hfill 
\scriptsize{Jacob M Potter} \hfill 
\scriptsize{Made in \LaTeX}

\end{document}
