\documentclass[line,margin]{res} 
\usepackage{hyperref}
\textheight=700pt
\begin{document}
\name{\Huge{Jacob M Potter} \normalsize{\sl Software Engineer}}
\begin{resume}

%-------------------------------------------------------------------------------
%   OBJECTIVE
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
Obtain a challenging computing co-op or internship for the spring of 2019.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
\section{CONTACT}
{jmp1617@rit.edu}\hfill 
{jacob-potter.com}\\
(413) 335-7767\hfill 
{github.com/jmp1617}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Rochester Institute of Technology}, Rochester, NY\hfill
    \textbf{2016-2021}\\
{\sl Bachelor of Science}, Computer Science, May 2021\hfill GPA: 3.50
\\
{\sl Dean's List} - Golisano College of Computing and Information Sciences
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   PROJECTS SECTION
%-------------------------------------------------------------------------------
\section{PROJECTS}
\par
    {\textbf{IPv4Lib}}
    {\sl (C)}{\sl (github.com/jmp1617/IPv4PI)}\hfill \textbf{Active Project}\\ 
    Library and payload injection framework for the IPv4 spec. Currently 
    supports IPv4, Ethernet II (including fcs), and the TCP and UDP suite. Loads 
    in a packet from either a file or a raw socket (bypassing the normal 
    TCP/IP protocols).
\par
    {\textbf{Deepnet}}
    {\sl (C, OpenGL)}{\sl (github.com/jmp1617/deepnet)}\hfill \textbf{2017}\\ 
    Multi-purpose four layer CLI deep learning neural network. Uses
    backpropagation and sigmoid activation. Features include importing and 
    exporting trained synapses and live OpenGL synapse delta visualization.
\par
    {\textbf{MIPS R2K module analyzer/editor}}
    {\sl (C)}{\sl (github.com/jmp1617/lmedit)}\hfill \textbf{2017}\\
    Reads all sections of R2K load or object module into dynamic memory, 
    extracts the data, and then displays in human readable form. Provides the 
    option to edit the binary data in place and then write it out.
\par
    {\textbf{L.L.U.V.}}
    {\sl (Python 3.5)}{\sl (github.com/jmp1617/LLUV)}\hfill \textbf{2017}\\ 
    L.L.U.V. (Linux Live USB Vending) is an easy to use front-end TUI for the 
    Linux command dd. Published on Python Pip. Uses npyscreen for graphics.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   COMPUTER SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}
\textbf{Languages}: C 99, Python (2.7-3.5), Java 8, MIPS Assembly (32 bit).
\\
\textbf{Networking and Security}: Cisco-3550, Wireshark, Nmap, Metasploit.  
\\
\textbf{Compilers and Tools}: GCC, Clang, GDB, Vim, Valgrind, Git, 
Jetbrains Suite. 
\\
\textbf{Operating Systems}: 
GNU+Linux, Mac OSX, Windows, IOS, Android.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
\section{EXPERIENCE}
\employer{\textbf{Summer 2017}}
\location{Southwick, MA}
\dates{{\sl Whalley Computer Associates}}
\title{\textbf{Receiving Department}}
\begin{position}
    Responsible for receiving and inventory of high dollar value 
    computational products for customers. Customer base ranged from large 
    corporate institutions to medium computing security companies. Worked in a
    team based corporate environment.
\end{position}
\employer{\textbf{Summer 2016}}
\location{Belchertown, MA}
\dates{{\sl Belchertown IT Department}}
\title{\textbf{IT Intern}}
\begin{position}
    Tasked with repairing computational devices, imaging and setting up devices, 
    as well as assisting school staff with both hardware and software issues. 
    Planned and implemented the student help desk system for the high 
    school.
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
\section{ACTIVITIES}
{\textbf{Computer Science House}}
{\sl (organization)}{\sl (csh.rit.edu)}\hfill
\textbf{Current Member}\\
A special interest house at RIT which encourages group collaboration on technical 
projects and provides access and funds to develop those projects.\\
\textbf{Events}: 
CRTS (Red team - Blue team), Opcommation (Networking Hackathon).\\\\
\textbf{Other Interests/Activities}\\
MLH Brick Hack, Geocaching, Snowboarding, Archery, Lock picking, Biking, Hiking.
%-------------------------------------------------------------------------------

\end{resume}
\scriptsize{References on request} \hfill 
\scriptsize{Jacob M Potter} \hfill 
\scriptsize{Made in \LaTeX}
\end{document}
